\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}
\usepackage{graphicx}
\definecolor{pank}{RGB}{245, 86, 133}

\renewcommand{\hyphenpenalty}{10000}
\renewcommand{\exhyphenpenalty}{10000}

\begin{document}

\part{Fatema H. Boxwala}

\section{Education}

\begin{yearlist}

\item[Honours Bachelor of CS]{2014 -- present}
     {University of Waterloo}
     {Waterloo, ON}

\end{yearlist}

\section{Awards}
\begin{factlist}
\item{2016}{Federation of Students Leadership Award}
\item{2016}{WPIRG Community Builders Bursary}
\item{2014}{University of Waterloo President's Scholarship}
\end{factlist}

\section{Experience}

\begin{eventlist}

\item{May 2016 -- August 2016}
     {Rackspace Managed Security, San Antonio}
     {Software Developer}

Worked on a team developing software used by security analysts to secure 
dedicated and cloud-based servers, primarily written in \textcolor{pank}{Python}.
Gained valuable experience working with \textcolor{pank}{AWS}, Azure, and Rackspace dedicated servers.
Collaborated and communicated on a fully remote team.

\item{August 2015 -- December 2015}
    {PointClickCare, Mississuaga}
    {Testing Analyst}
    
Learned to program in Visual Basic, troubleshoot client problems, 
and perform \textcolor{pank}{root-cause analysis} of software bugs. Monitored
hourly error reports, resolved support cases, communicated 
with clients, and wrote scripts and macros in \textcolor{pank}{VB and Bash}
to reduce manual tasks.

\item{September 2014 -- August 2015}
     {CATT, Waterloo}
     {Technical Assistant}

Performed all technical tasks for an on-campus civil engineering research
centre. This included maintaining three websites: 
\href{http://catt.ca}{catt.ca}, 
\href{http://canadiantrenchlessdirectory.ca}{canadiantrenchlessdirectory.ca}, 
\href{http://roadshow2015.cattevents.ca}{cattroadshow2015.ca}, and three
\textcolor{pank}{Windows} computers.

\item{January 2015 -- Present}
     {Women in CS Undergraduate Committee, Waterloo}
     {Chair}

Served as Chair and External Liaison, represented the committee publicly, and 
maintained relations with external groups. I developed my
\textcolor{pank}{public speaking} and communication skills greatly. 
Also \textcolor{pank}{managed} other members of the 
committee, and through this I grew as a team leader.
As a member of the systems-committee I learned about \textcolor{pank}{Linux}
systems administration and mentored other systems volunteers.

\end{eventlist}

\personal
[fboxwala.github.io]
{ca.linkedin.com/in/fatemaboxwala}
    {(416)-970-9113}
    {fatema.boxwala@uwaterloo.ca}

\section{Technical skills}

\begin{factlist}

\item{Languages}
     {C, C++, Racket, Bash, Python, Visual Basic, HTML/Markdown, CSS/Sass, JavaScript,  MIPS}

\item{Utilities}
     {AWS, Git, Linux, Jekyll, \LaTeX, Pelican, Wordpress, Android Studio, GIMP, Windows}

\item{Miscellaneous}
    {Testing, Debugging, Troubleshooting, UI Design, Root-cause analysis}

\end{factlist}

\section{Professional skills}

\begin{factlist}
\item{Languages}{French, Gujarati, Hindi, Urdu}
\item{Management}{Conflict resolution, delegating and organizational skills,
    developed through many years of leadership}
\item{Communication}{Public speaking, professional writing, policy development}
\end{factlist}

\section{Projects}

\begin{yearlist}

\item{}
    {WiCS Website (\href{http://wics.uwaterloo.ca}{wics.uwaterloo.ca})}
    {Developer for our official committee website, hosted on 
    \href{http://github.com/wics-uw/website}{github}.}\smallskip\\

\item{}
    {Git and Open Source Workshop (\href{http://github.com/wics-uw/git-workshop-w16}{git-workshop-w16})}
    {Curriculum developed for an introductory workshop to Git, Github and Open
        source technology. I both developed the curriculum and taught the first
    iteration of the workshop.}\smallskip\\

\item{}
     {CanIPass Android Application}
     {Small application developed in \textcolor{pank}{Android Studio} for calculating a marks
     and progress in courses with multiple components.}\smallskip\\

\item{}
    {Personal Website (\href{http://fboxwala.github.io}{fboxwala.github.io})}
     {Website containing my resume, projects and contact info. Hosted on 
     \href{http://github.com/fboxwala/fboxwala.github.io}{github}, and powered
 by \textcolor{pank}{Jekyll}}\smallskip\\

 \item{}
     {CC3K Rogue-Like}
     {Rogue-like game developed in \textcolor{pank}{C++}, played in a terminal. Built as a 
         group project for CS246, "Object-oriented Software Development}

 \end{yearlist}

 \end{document}

%
